Automated Synthesis of State-Space Digital Systems

### 2016-11-28 cav2017/cav2017.tex
add experimental evaluation section
Description of Benchmarks

%-------------------------------
\section{Introduction}
%-------------------------------
In this paper we formalise the notion of solution generalisation for CEGIS. 
This technique allows the inductive generalisation engine to look for 
candidate solutions in a reduced solution space.

\section{Counter-Example Guided Inductive Synthesis with solution generalisation}

@@

\section{Discretising Continuous Space Dynamics}

@@

\section{LTI representations of ARMA models}

@@

\section{Related Work}

>>>>

%-------------------------------
\section{Introduction}
%-------------------------------

In this paper we formalise the notion of solution generalisation for CEGIS. 
This technique allows the inductive generalisation engine to look for 
candidate solutions in a reduced solution space.

%-------------------------------
\section{Counter-Example Guided Inductive Synthesis with solution generalisation}
%-------------------------------

@@

%-------------------------------
\section{Discretising Continuous Space Dynamics}
%-------------------------------

@@

%-------------------------------
\section{LTI representations of ARMA models}
%-------------------------------

@@

%-------------------------------
\section{Experimental Evaluation}
%-------------------------------

%-------------------------------
\subsection{Description of the Benchmarks}
%-------------------------------

A set of state-space models for different classes of systems were extracted from the literature and employed for validating our automated synthesis methodology. All the systems are SISO models of the following form:
\begin{equation}
\left\lbrace\begin{array}{c}
\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
\end{array}\right.
\end{equation}

The first plant represents a DC motor position model from~\cite{CTMS}. It is a third order system and presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
$$
\textbf{A}=\left[\begin{array}{ccc}
0		& 1 		& 0						\\
0 		& -1.087	& 8587					\\
0		& -9964		& -1.455\times 10^{6}	\\
\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
0 \\ 0 \\ -1.455\times10^{6}
\end{array}\right]
$$
%
$$
\textbf{C}=\left[\begin{array}{ccc}
1 & 0 & 0\\
\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
\theta \\ \dot{\theta} \\ i \\
\end{array}\right],
$$
where the states $\theta$, $\dot{\theta}$, and $i$ are respectively the rotor angular position, rotor angular rate and the current of armature. The DC motor is stable in open loop.

The second benchmark is an aircraft pitch dynamics model extracted from~\cite{CTMS}. It is a third order system and it presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
$$
\textbf{A}=\left[\begin{array}{ccc}
-0.313	& 56.7 		& 0		\\
-0.0139	& -0.426	& 0		\\
0		& 56.7		& 0		\\
\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
0.232 \\ 0.0203 \\ 0
\end{array}\right]
$$
%
$$
\textbf{C}=\left[\begin{array}{ccc}
0 & 0 & 1\\
\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
\alpha \\ \dot{\theta} \\ \theta \\
\end{array}\right],
$$
where the states $\alpha$, $\dot{\theta}$, and $\theta$ are respectively the aircraft attack angle, pitch rate and the pitch angle. The aircraft pitch dynamic is critically stable in open loop, with a pole in origin of $s$-plane.

The third benchmark is an ball magnetic levitation model extracted from~\cite{maglev}. It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
$$
\textbf{A}=\left[\begin{array}{ccc}
0		& 1 		& 0		\\
1752	& 0			& -34.07\\
0		& 0			& -38.27\\
\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
0 \\ 0 \\ 1.923
\end{array}\right]
$$
%
$$
\textbf{C}=\left[\begin{array}{ccc}
1 & 0 & 0\\
\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
z \\ \dot{z} \\ i \\
\end{array}\right],
$$
where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.

The remaining of benchmarks represents classic DC-DC converters: buck, boost, and buck-boost. They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
i_{L} \\ v_{C}\\
\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor. The matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, and $\textbf{D}$ for the buck converter are:
$$
\textbf{A}=\left[\begin{array}{cc}
0		& -500 \\
4545	& -1515\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
125 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 1\\
\end{array}\right],~ \textbf{D}= 0.
$$

The matrices of the boost converter are:
$$
\textbf{A}=\left[\begin{array}{cc}
0		& -375 \\
3409	& -1515\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
500 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 1\\
\end{array}\right],~ \textbf{D}= 0.
$$

Finally, the matrices of the buck-boost converter are:
$$
\textbf{A}=\left[\begin{array}{cc}
0		& 375 \\
-3409	& -1515\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
125 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 1\\
\end{array}\right],~ \textbf{D}= 0.
$$.

%-------------------------------
\subsection{Objectives}
%-------------------------------

%-------------------------------
\subsection{Results}
%-------------------------------

%-------------------------------
\subsection{Threats to validity}
%-------------------------------

%-------------------------------
\section{Related Work}
%-------------------------------
